Planarity and Street Network Representation in Urban Form Analysis

### 2018-02-19 main.tex
update fig, table folders

\begin{figure}[tbp]
	\includegraphics[width=0.48\textwidth]{figures_tables/planar_vs_not_labels.png}
	\caption{Spatial network examples. Gray lines = edges (i.e., street segments), circles = nodes (i.e., intersections and dead ends), red dots = two-dimensional line crossings (i.e., artificial nodes in planar representation).}
	\label{fig:planar_vs_not}
\end{figure}

@@

\begin{table*}[htbp]
	\centering
	\caption{Planarity measures for central street networks in 50 cities worldwide (Planar = whether street network passed the formal test of planarity; $\phi$ = Spatial Planarity Ratio; $\lambda$ = Edge Length Ratio).}
	\label{tab:world_cities}
	\input{figures_tables/table_world_cities.tex}
\end{table*}

\begin{figure*}[htbp]
	\centering
	\includegraphics[width=\textwidth]{figures_tables/world_map_bw.png}
	\caption{Map of world cities from Table \ref{tab:world_cities} grouped by drivable $\phi$ terciles (lower values mean less planar).}
	\label{fig:world_map_bw}
\end{figure*}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{figures_tables/regression_lambda_phi_linear.png}
	\caption{Plot of $\lambda$ vs $\phi$ by network type with regression lines.}
	\label{fig:regression_lambda_phi}
\end{figure}

@@

\begin{table}[htbp]
	\centering
	\caption{Summary statistics of planarity indicators across 100 square-mile samples of Oakland, California's drivable network.}
	\label{tab:samples_city}
	\input{figures_tables/table_samples_city.tex}
\end{table}

>>>>

\begin{figure}[tbp]
	\includegraphics[width=0.48\textwidth]{figures/planar_vs_not_labels.png}
	\caption{Spatial network examples. Gray lines = edges (i.e., street segments), circles = nodes (i.e., intersections and dead ends), red dots = two-dimensional line crossings (i.e., artificial nodes in planar representation).}
	\label{fig:planar_vs_not}
\end{figure}

@@

\begin{table*}[htbp]
	\centering
	\caption{Planarity measures for central street networks in 50 cities worldwide (Planar = whether street network passed the formal test of planarity; $\phi$ = Spatial Planarity Ratio; $\lambda$ = Edge Length Ratio).}
	\label{tab:world_cities}
	\input{tables/table_world_cities.tex}
\end{table*}

\begin{figure*}[htbp]
	\centering
	\includegraphics[width=\textwidth]{figures/world_map_bw.png}
	\caption{Map of world cities from Table \ref{tab:world_cities} grouped by drivable $\phi$ terciles (lower values mean less planar).}
	\label{fig:world_map_bw}
\end{figure*}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{figures/regression_lambda_phi_linear.png}
	\caption{Plot of $\lambda$ vs $\phi$ by network type with regression lines.}
	\label{fig:regression_lambda_phi}
\end{figure}

@@

\begin{table}[htbp]
	\centering
	\caption{Summary statistics of planarity indicators across 100 square-mile samples of Oakland, California's drivable network.}
	\label{tab:samples_city}
	\input{tables/table_samples_city.tex}
\end{table}
